\Large \bf Frontrunning

### 2018-08-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Historical Context draft + adding related documents

\subsection{Historical Context}
Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978cboe}
\end{quote}

@@

On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
\begin{quote}
it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote} 
% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.

%@shayan complete the historical context

\subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc. In the blockchain world, everyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain. Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.

>>>>

\subsection{Historical Context}
Frontrunning was first appeared on the Chicago Board Options Exchange (CBoE) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg CBoE) and SEC to regulate, detect and define laws and regulations to deal with frontrunning~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote}

As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, CBoE and other exchanges (and brokers) issued educational circulars for their members asserting that frontrunning violates existing rules, with some examples of what is considered frontrunning. However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.

Further reading on the early details on the history and challenges of detecting and regulating frontrunning can be found in~\cite{markham1988front} . % TODO: add a more recent publication here as well!

Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunnning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{finra_2012, sec2012frontrunning}.

\subsection{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc. In the blockchain world, anyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain. Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however a decentral application could be designed in such a way to mitigate frontrunning attacks.
